Unigram entropy in childes

### 2018-08-23 Unigram Positional Entropy.Rmd
Added Mandarin unigram entropy computations

>>>>

```{r Chinese Unigram Entropy}
zhou_dinner <- get_utterances(corpus = "zhoudinner")

get_chinese_entropies <- function(role, sen_length, utterances) {

  if(role == "Target_Child") {
    sub_utterances <- utterances %>%
      filter(speaker_role == "Target_Child") %>%
      filter(gloss != "") %>% 
      mutate(length = str_count(stem, " ") + 1) 
  } else {
     sub_utterances <- utterances %>%
      filter(speaker_role != "Target_Child") %>%
      filter(speaker_role != "") %>% 
      mutate(length = str_count(stem, " ") + 1)
  }

entropies <- map(2:10, ~get_chinese_entropies("not child", .x, zhou_dinner)) %>%
  bind_rows() %>% filter(word_order <= length) #some utterances have "" counted for word_order

ggplot(entropies, aes(x = word_order, y = empirical_entropy,
                      ymin = ci_lower, ymax = ci_upper)) +
  facet_wrap(~ length) + 
  geom_pointrange() +
  geom_smooth(se = F) +
  ggtitle("Adult Unigram Entropy vs. Word Position (Mandarin Zhou Dinner Corpus)")

entropies_child <- map(2:10, ~ get_chinese_entropies("Target_Child", .x, zhou_dinner)) %>%
  bind_rows() %>% filter(word_order <= length)

ggplot(entropies_child, aes(x = word_order, y = empirical_entropy,
                      ymin = ci_lower, ymax = ci_upper)) +
  facet_wrap(~ length) + 
  geom_pointrange() +
  geom_smooth(se = F) +
  ggtitle("Child Unigram Entropy vs. Word Position (Mandarin Zhou Dinner Corpus)")

ggplot(entropies_all, aes(x = word_order, y = empirical_entropy,
                      ymin = ci_lower, ymax = ci_upper, color = role)) +
  facet_wrap(~ length) + 
  geom_pointrange(position = position_dodge(.25)) +
  geom_smooth(se = F) +
  ggtitle("Adult and Child Unigram Entropy vs. Word Position (Mandarin Zhou Dinner Corpus)")
```
